### 2020-09-21 response-to-reviews.txt

COMMENTS TO THE AUTHOR:

Reviewer #1: The paper describes a modification to the FrodoKEM scheme using Trivium instead of SHAKE as PRNG that gives a significant speedup for a hardware implementation.

Editorial:

The paper is not well written. There are several grammatical errors, odd sentences, and strange phrases. Often, there is a mix-up between singular and plural between article, noun, and verb (see, e.g., page 2, left column, lines 31 and 32). Furthermore, there are frequently words missing in sentences (see, e.g., page 2, left column, line 59). The authors must apply proof reading; this is not the job a the reviewers.
Floating figures should use top [t] placement; several times, there are short text parts in between figures, making the paper hard to read.
Several times, lines are too long and leap into white space.

Title:

The title of the paper does not fit to its contents.

- There is no design space exploration: There is no rationale, why Trivium was picked and not another hash function. This question is simply dismissed on page 5, right column, lines 6f. The only exploration vector is the degree of parallelism.

- The work is not on lattice-based KEMs in general as the title suggests but focuses on FrodoKEM. The suggested design changes are likely to apply to any other cryptographic scheme who's performance heavily depends on a hash function - but this question is not discussed in detail.

A more accurate title would be "Replacing SHAKE with Trivium in FrodoKEM for better performance and scalability" or so.

Detailed Feedback:

- Section 2.1: The hardware implementation of XMSS by Wang et. al. is missing [1] in the related work.

- Table 1: The unit of throughput is missing (last column).

- Section 3: There are several redundant text blocks in the beginning of the section (first two paragraphs).

- Section 3, page 5, left column, lines 36-39, "Moreover, parallelisations was not possible for this design, as this would require a faster SHAKE design, increasing the area consumption by 3-8x [3].": Instead of using a faster SHAKE design, one could use several SHAKE instances (just as you do with Trivium) - at high cost, but likely feasible.

- Section 3.1: Is your design a new implementation or directly based on the code from reference [9]?

- Section 3.1, matrix operations (page 6, lines 20-27, left and right column): You are lacking references to prior work in matrix-matrix and matrix-vector multiplication in hardware as well as parallelization techniques for matrix operations. These are well known and well researched areas.

- Section 3.1, page 6, lines 38-40: You replaced the PRNG(s) with Trivium; why do you still keep a SHAKE core for calculating the shared secret? Why not go for Trivium altogether?

- Section 3.2: You claim that your first-order masking does not affect runtime - but in my understanding, you need two parallel instances for that. Therefore, either time or area is affected by your masking approach. Please clarify.

- Section 4: Please discuss how your approach and parallelization affects the time-area product; add the time-area product to the tables.

- Section 4: Please add a direct comparison in regards to throughput, latency, and area consumption between Trivium and the two SHAKE versions that are discussed.

- Section 4: Please describe your implementations with and without BRAM more clearly. What alternative resources are used when BRAM is avoided? LUT-memory? Registers?

- Section 4, page 7, right column, lines 56f - "For decapsulation, we save between 1.6x and 2.6x slices when BRAM is used...": Be precise - is it more or less slices?

- Section 5: The first sentence is incorrect; due to your modifications, you are not evaluating the performance of FrodoKEM as submitted to NIST.

- Section 5: The contents of this section are entirely redundant.

In Section 1 (page 2, left column, line 43) and Section 3 (page 5,lines 51-56), you claim that by replacing SHAKE with Trivium the security of FrodoKEM still holds. This claim needs a proof.

[1] https://eprint.iacr.org/2018/1225

Reviewer #2: This paper proposes a more efficient and high(er) throughput design for FRODOKEM, a NIST post-quantum standardization candidate (at Round-2). The authors have two main extensions to the prior work (some include the authors of this journal). First, they notice that one of the key drawbacks of the prior designs were using an AES or SHAKE cipher based designs for random number generators. The authors instead use TRIVIUM, which is known to be more hardware efficient. The authors then accelerate the hardware design using parallel multipliers for the other compute bottleneck of matrix multiplication with relatively straightforward methods. The second extension is using masking to prevent first-order side-channel attacks. The design work is intensive despite being fairly obvious extensions. The editorial quality is high. But there are several critical issues described below causing me to request a major revision.

The authors argue that TRIVIUM provides similar security as of AES. But I believe TRIVIUM provides 80-bit security pre-quantum and potentially even lower security under quantum computer attacks. How is that addressing NIST's security levels? There is no discussion of these aspects. Also, despite NIST's recommendations, the authors use TRIVIUM and justify this based on other's work (some written by these authors) and that NIST's idea may change, which are controversial claims. But this second issue is less severe than my first criticism.

The proposed masking scheme is not validated and is arguably vulnerable. The split shares are combined in Step 5 of Algorithm 3, in a direct/unprotected manner. Therefore, the attacker can target this part where the shares are combined to directly correlate power measurements to the secret key. Moreover, there is no validation of side-channel security, e.g., through TVLA. This is a critical issue as a similar line of work using additive homomorphism (see Reparaz et al. PQ-2016) has shown a surprising vulnerability despite masking.

Related to side-channel discussions, the work in [5], discusses single-trace side-channel attacks, which cannot be mitigated with masking. The authors omit this aspect of the work and do not discuss/demonstrate potential countermeasures against it. I would also add the work by Aysu et al. HOST-18, which forms the basis of [5] applied to an earlier version of Frodo.

The work's impact can be significantly enhanced by showing the gains at a system level. The original Frodo paper CCS 2016, demonstrate the impact Frodo on an HTTPS/TLS connection. Estimating from their numbers, what would be an expected gain on the overall protocol with the proposed acceleration techniques?

The community can greatly benefit from an open-source design of this work. Do the authors plan on sharing their codes after a publication?

Reviewer #3: The authors have presented a high-throughput FPGA implementation of Frodo CCA-KEM. Their proposed design uses parallel multipliers to speed up matrix multiplication and Trivium PRNG for fast sampling in low area. The decapsulation step is also masked against power side-channel attacks. Overall speedup of 14-16x is achieved compared to previous work.

(1) Section 2.2 - "FrodoKEM comes with two parameter sets FrodoKEM-640 and FrodoKEM-976" - Since Round 2 last year, Frodo offers a third parameter set Frodo-1344. Can the proposed design be scaled for this? Any particular reason this was not evaluated, such as resource limitations on the Artix-7 FPGA?

(2) Section 2.2 - "The matrices generated heavily utilize PRNGs, suggested by the authors via AES or SHAKE. The output of these algorithms have nice statistical properties, but the overhead required to achieve this is high" - What are the statistical properties required from the PRNG used for sampling in Frodo? Does Trivium not have those statistical properties?

(3) The side-channel sections (Sections 2.4 and 3.2) need to be organized better. Please provide the masked version of M = C - B'S in the Algorithm format. Also, please provide a pictorial explanation of how multiplication by shares of S is performed in parallel by the proposed design without affecting throughput and how the row-column combinations are scheduled to prevent leakage.

(4) Section 4 - "When compared to cSHAKE, the PRNG previously used in literature, Trivium (the PRNG we propose to use), occupies 4.5x less area on the FPGA (measured in slices)" - cSHAKE produces 1344 or 1088 bits per round (depending on whether SHAKE-128 or SHAKE-256 is used) but each Trivium core in the proposed design produces 32 bits per round. So, when using 4 / 8 / 16 multipliers, which corresponds to 2 / 4 / 8 Trivium cores, the total number of bits is much less than cSHAKE but the area becomes equal to cSHAKE for 4 Trivium cores and greater than cSHAKE for 8 Trivium cores. Then, what is the advantage of using Trivium instead of cSHAKE when using many parallel multipliers?

(5) Could you please compare the resource consumption of the Frodo implementation with 4 / 8 / 16 multipliers with cSHAKE + AES? Tables 3, 4, 5 compare the proposed design only with the single multiplier case. It is more important to understand the parallel multiplier case. Since cSHAKE and AES produce greater number of bits per round, it will probably still need one cSHAKE core and 1 or 2 AES cores. Right now, it is difficult to extrapolate the overall area requirement from Table 6 alone.

(6) Is step 14 in Algorithm 3 (the FO transform comparison step) implemented in constant time? A recent paper (published after this manuscript was submitted) uses timing leakage in this step to attack software implementation of Frodo CCA: Guo et al., "A key-recovery timing attack on post-quantum primitives using the Fujisaki-Okamoto transformation and its application on FrodoKEM", ePrint 2020/743. Is the proposed design secure against this attack?

(7) To make the side-channel section more complete, could you please provide a brief outline of how one can go about verifying the effectiveness of the proposed masking scheme?

__

### 2020-09-21 response-to-reviews.txt

Reviewer #1: The paper describes a modification to the FrodoKEM scheme using Trivium instead of SHAKE as PRNG that gives a significant speedup for a hardware implementation.

Editorial:

The paper is not well written. There are several grammatical errors, odd sentences, and strange phrases. Often, there is a mix-up between singular and plural between article, noun, and verb (see, e.g., page 2, left column, lines 31 and 32). Furthermore, there are frequently words missing in sentences (see, e.g., page 2, left column, line 59). The authors must apply proof reading; this is not the job a the reviewers.
Floating figures should use top [t] placement; several times, there are short text parts in between figures, making the paper hard to read.
Several times, lines are too long and leap into white space.

Response: We have done a thorough proof reading of the paper to correct these errors.

@@

Title:

The title of the paper does not fit to its contents.

- There is no design space exploration: There is no rationale, why Trivium was picked and not another hash function. This question is simply dismissed on page 5, right column, lines 6f. The only exploration vector is the degree of parallelism.

Response: We have a new title which better suits the content of the paper.

@@

- The work is not on lattice-based KEMs in general as the title suggests but focuses on FrodoKEM. The suggested design changes are likely to apply to any other cryptographic scheme who's performance heavily depends on a hash function - but this question is not discussed in detail.

Response: This is true, but the research can also be used on any standard LWE-based cryptographic scheme (in fact any scheme that requires matrix multiplication) which is why we state this in the title.

@@

A more accurate title would be "Replacing SHAKE with Trivium in FrodoKEM for better performance and scalability" or so.

Detailed Feedback:

- Section 2.1: The hardware implementation of XMSS by Wang et. al. is missing [1] in the related work.

Response: We restricted Table 1 to only include NIST PQC candidates.

@@

- Section 3, page 5, left column, lines 36-39, "Moreover, parallelisations was not possible for this design, as this would require a faster SHAKE design, increasing the area consumption by 3-8x [3].": Instead of using a faster SHAKE design, one could use several SHAKE instances (just as you do with Trivium) - at high cost, but likely feasible.

Response: We add a sentence to cover this case as well.

- Section 3.1: Is your design a new implementation or directly based on the code from reference [9]?

Response: The designs here are inspired by [9] but the code is new.

@@

- Section 3.1, matrix operations (page 6, lines 20-27, left and right column): You are lacking references to prior work in matrix-matrix and matrix-vector multiplication in hardware as well as parallelization techniques for matrix operations. These are well known and well researched areas.

Response: We added a sentence for this with some references.

@@

- Section 3.1, page 6, lines 38-40: You replaced the PRNG(s) with Trivium; why do you still keep a SHAKE core for calculating the shared secret? Why not go for Trivium altogether?

Response: Using Trivium/SHAKE for generating the randomness constitutes >>90% of its overall use, which was the motivation for this paper and using Trivium here we see significant savings. By using a small SHAKE core here we are more complient with the FrodoKEM specifications and moreover the calculation of the shared secret is not in the critical path of the hardware design so we are thus able to start the next KEM operations (which would not be possible if we wanted to use the Triviums already there).

@@

- Section 3.2: You claim that your first-order masking does not affect runtime - but in my understanding, you need two parallel instances for that. Therefore, either time or area is affected by your masking approach. Please clarify.

Response: Yes, as it's parallelised the area is affected but we can do this 'for free' because it already exists in hardware for use in other parts of the KEM algorithms. We added a sentence to make this more clear.

@@

- Section 4: Please discuss how your approach and parallelization affects the time-area product; add the time-area product to the tables.

Response: Thanks for this idea, it has now been added.

- Section 4: Please add a direct comparison in regards to throughput, latency, and area consumption between Trivium and the two SHAKE versions that are discussed.

Response: We added another paragraph using the area-time metric to further compare the Trivium and SHAKE versions.

@@

- Section 4: Please describe your implementations with and without BRAM more clearly. What alternative resources are used when BRAM is avoided? LUT-memory? Registers?

Response: We add a footnote in the results section to explain how we synthesised the hardware design to ensure no BRAMs were used.

@@

- Section 5: The first sentence is incorrect; due to your modifications, you are not evaluating the performance of FrodoKEM as submitted to NIST.

Response: Thanks, this has now been corrected.

- Section 5: The contents of this section are entirely redundant.

Response: The purpose of this section is to conclude and summary the contributions of the paper.

@@

In Section 1 (page 2, left column, line 43) and Section 3 (page 5,lines 51-56), you claim that by replacing SHAKE with Trivium the security of FrodoKEM still holds. This claim needs a proof.

Response: We believe this may be out of the scope for this paper. We aimed to investigate the performance potential of FrodoKEM with a fast PRNG in hardware.

### 2020-09-21 tex/abstract.tex
corrected the paper to suit comments from Reviewer 1, also updated this in the response to reviewers txt file

FrodoKEM is a lattice-based key encapsulation mechanism, currently a semi-finalist in NIST’s post-quantum standardization effort. A condition for these candidates is to use NIST standards for PRNG /
seed-expanding, and as such most candidates utilize SHAKE, an XOF defined in the SHA-3 standard. However, for many of the candidates, this module is a significant implementation bottleneck. Trivium is a lightweight, ISO standard stream cipher which performs well in hardware and has been used in previous hardware designs for lattice-based cryptography. This research proposes optimized designs for FrodoKEM, concentrating on high throughput by parallelising the matrix multiplication operations within the cryptographic scheme. This process is eased by the use of Trivium due to its higher throughput and lower area consumption. The parallelisations proposed also complement the addition
of first-order masking to the decapsulation module. Overall, we significantly increase the throughput of FrodoKEM; for encapsulation we see a 16x speed-up, achieving 825 operations per second, and for decapsulation we see a 14x speed-up, achieving 763 operations per second, compared to the previous state-of-the-art, whilst also maintaining a similar FPGA area footprint of less than 2000 slices.

>>>>

FrodoKEM is a lattice-based key encapsulation mechanism, currently a semi-finalist in NIST’s post-quantum standardization effort. A condition for these candidates is to use NIST standards for PRNG (i.e., seed-expanding), and as such most candidates utilize SHAKE, an XOF defined in the SHA-3 standard. However, for many of the candidates, this module is a significant implementation bottleneck. Trivium is a lightweight, ISO standard stream cipher which performs well in hardware and has been used in previous hardware designs for lattice-based cryptography. This research proposes optimized designs for FrodoKEM, concentrating on high throughput by parallelising the matrix multiplication operations within the cryptographic scheme. This process is eased by the use of Trivium due to its higher throughput and lower area consumption. The parallelisations proposed also complement the addition
of first-order masking to the decapsulation module. Overall, we significantly increase the throughput of FrodoKEM; for encapsulation we see a 16x speed-up, achieving 825 operations per second, and for decapsulation we see a 14x speed-up, achieving 763 operations per second, compared to the previous state-of-the-art, whilst also maintaining a similar FPGA area footprint of less than 2000 slices.

### 2020-09-21 tex/conclusions.tex
corrected the paper to suit comments from Reviewer 1, also updated this in the response to reviewers txt file

The main contributions of this research is to evaluate the lattice-based KEM and potential NIST post-quantum standard, FrodoKEM \cite{frodokem}, in hardware. We develop designs which can reach up to 825 operations per second, where most of the designs fit in under 1500 slices. Area consumption results are less than the previous state-of-the-art, and are much lower than many of the other post-quantum hardware designs shown in Table \ref{tab:pqc}. We significantly improve the throughput performance compared to the state-of-the-art, by increasing the number of parallel multipliers we use during matrix multiplication. In order to do this efficiently, we replace an inefficient PRNG previously used, cSHAKE, with a much faster and smaller PRNG, Trivium. As a result, we are able to obtain either a much lower FPGA footprint (up to 5x smaller) or a much higher throughput (up to 16x faster) compared to previous research. Our implementations run in constant computational time and the designs comply with the Round 2 version of FrodoKEM in all aspects except for this PRNG choice. To further evaluate the performance of FrodoKEM, we implemented first-order masking for decapsulation, and we showed that it can be achieved with almost no effect on performance.

>>>>

The main contributions of this research is to evaluate the performance potential of FrodoKEM \cite{frodokem}, a NIST post-quantum candidate for key encapsulation, when utilising a significantly more performant PRNG in hardware. We develop designs which can reach up to 825 operations per second, where most of the designs fit in under 1500 slices. Area consumption results are less than the previous state-of-the-art, and are much lower than many of the other post-quantum hardware designs shown in Table \ref{tab:pqc}. We significantly improve the throughput performance compared to the state-of-the-art, by increasing the number of parallel multipliers we use during matrix multiplication. In order to do this efficiently, we replace an inefficient PRNG previously used, cSHAKE, with a much faster and smaller PRNG, Trivium. As a result, we are able to obtain either a much lower FPGA footprint (up to 5x smaller) or a much higher throughput (up to 16x faster) compared to previous research. Our implementations run in constant computational time and the designs comply with the Round 2 version of FrodoKEM in all aspects except for this PRNG choice. To further evaluate the performance of FrodoKEM, we implemented first-order masking for decapsulation, and we showed that it can be achieved with almost no effect on performance.

### 2020-09-21 tex/design.tex
corrected the paper to suit comments from Reviewer 1, also updated this in the response to reviewers txt file

As described in Section \ref{sec:related}, FrodoKEM requires heavy use of PRNG / seed expanding. In the algorithm specifications, it is suggested to use either SHAKE or AES. In particular, the most computationally intensive operations, such as Line \ref{decapslwe} of Algorithm \ref{alg:decaps}, require 410k or 953k 16-bit pseudo-random values, depending on the parameter set used. In order for PRNG not to be the bottle-neck it needs to achieve a very high throughput (ideally with relatively low area consumption) typically in the range of 16 bits per clock cycle. In a previous hardware design, proposed by Howe et al. \cite{howe2018standard}, high throughput for the PRNG was achieved by pre-calculating randomness and storing it in BRAM. Random data newly calculated was then written into the memory, overwriting the random data previously stored. This is an efficient approach, however a more efficient PRNG that would not require BRAM usage, potentially increasing the operating frequency of the design, and thus improve its throughput. Moreover, parallelisations was not possible for this design, as this would require a faster SHAKE design, increasing the area consumption by 3-8x \cite{bertoni2012keccak}. The area consumption of SHAKE (or AES) was an issue with the previous design. For example, cSHAKE used within FrodoKEM-640 Encaps occupies 42\% of the overall hardware resources~\cite{howe2018standard}.

@@

We implement first-order masking scheme (discussed in Section \ref{sec:mask}) to the decapsulation operation $\mathbf{M} = \mathbf{C} - \mathbf{B}'\mathbf{S}$, as this is the only instance where secret-key information is used. Our design allows us to implement this masking schema without affecting the area consumption or throughput. This is achieved by using the optimizations previously discussed. The matrix $\mathbf{S}$ is split using the same technique from Figure \ref{parallel} and our secret shares are generated by using the Trivium modules as a PRNG source. By computing these calculations in parallel, the masked calculation of $\mathbf{M}$ has the same run-time as the one needed to complete the calculation when masking is not used. We ensure that the same row-column operation during the matrix multiplication is not computed in each parallel operation, to circumvent any attack that might combine the power traces and essentially remove the masking.

>>>>

As described in Section \ref{sec:related}, FrodoKEM requires heavy use of PRNG / seed expanding. In the algorithm specifications, it is suggested to use either SHAKE or AES. In particular, the most computationally intensive operations, such as Line \ref{decapslwe} of Algorithm \ref{alg:decaps}, require 410k or 953k 16-bit pseudo-random values, depending on the parameter set used. In order for PRNG not to be the bottle-neck it needs to achieve a very high throughput (ideally with relatively low area consumption) typically in the range of 16 bits per clock cycle. In a previous hardware design, proposed by Howe et al. \cite{howe2018standard}, high throughput for the PRNG was achieved by pre-calculating randomness and storing it in BRAM. Random data newly calculated was then written into the memory, overwriting the random data previously stored. This is an efficient approach, however a more efficient PRNG that would not require BRAM usage, potentially increasing the operating frequency of the design, and thus improve its throughput. Moreover, parallelisations were not possible for this design, as this would either require a faster SHAKE design, increasing the area consumption by 3-8x \cite{bertoni2012keccak} or worse still having several SHAKE instances, incurring an even worse resource consumption overhead. The area consumption of SHAKE (or AES) was an issue with the previous hardware design. For example, cSHAKE used within FrodoKEM-640 Encaps occupies 42\% of the overall hardware resources~\cite{howe2018standard}.

@@

We implement first-order masking scheme (discussed in Section \ref{sec:mask}) to the decapsulation operation $\mathbf{M} = \mathbf{C} - \mathbf{B}'\mathbf{S}$, as this is the only instance where secret-key information is used. Our design allows us to implement this masking schema without affecting the area consumption or throughput. Essentially this is achieved by re-using the parallelised matrix multiplier used through the proposed hardware design for FrodoKEM. The matrix $\mathbf{S}$ is split using the same technique from Figure \ref{parallel} and our secret shares are generated by using the Trivium modules as a PRNG source. By computing these calculations in parallel, the masked calculation of $\mathbf{M}$ has the same run-time as the one needed to complete the calculation when masking is not used. We ensure that the same row-column operation during the matrix multiplication is not computed in each parallel operation, to circumvent any attack that might combine the power traces and essentially remove the masking.

### 2020-09-21 tex/intro.tex
corrected the paper to suit comments from Reviewer 1, also updated this in the response to reviewers txt file

To this end, this paper concentrates on FrodoKEM, a key encapsulation mechanism submitted to NIST as a potential post-quantum standard. FrodoKEM is a conservative candidate due to its hardness being based on standard lattices, as opposed to Ring/Module-LWE, thus having limited practical evaluations. Thus, we explore the possibility to efficiently implementing it in hardware and estimate the overhead of protection against power analysis attacks using first-order masking. To maximize the throughput, we rely on a parallelised implementations of the matrix multiplication. We also aim to have a relatively low FPGA area consumption. To be parallelised, however, the matrix multiplication requires the use of a smaller and more performant pseudo-random number generator. We propose to achieve the performance required for the PRNG by using Trivium, an international standard under ISO/IEC 29192-3 \cite{ISO} and selected as part of the eSTREAM project. We utilize this instead of AES or SHAKE, as per the FrodoKEM specifications. We do this as a design exploration study, but, all the security arguments from the specifications still apply.

>>>>

To this end, this paper concentrates on FrodoKEM, a key encapsulation mechanism submitted to NIST as a potential post-quantum standard. FrodoKEM is a conservative candidate due to its hardness being based on standard lattices, as opposed to Ring/Module-LWE, thus having limited practical evaluations. Thus, we explore the possibility to efficiently implementing it in hardware and estimate the overhead of protection against power analysis attacks using first-order masking. To maximize the throughput, we rely on a parallelised implementations of the matrix multiplication. Although we do not utilise specialised techniques for parallelising the matrix multiplication, there exists a lot of prior art in this area of research \cite{jang2002area,qasim2008proposed}. We also aim to have a relatively low FPGA area consumption. To be parallelised, however, the matrix multiplication requires the use of a smaller and more performant pseudo-random number generator. We propose to achieve the performance required for the PRNG by using Trivium, an international standard under ISO/IEC 29192-3 \cite{ISO} and selected as part of the eSTREAM project, specifically selected for its hardware performance\footnote{\url{https://www.ecrypt.eu.org/stream/e2-trivium.html}}. We utilize this instead of AES or SHAKE, as per the FrodoKEM specifications. We do this as a design exploration study and not (per se) as a recommendation; other alternative ciphers or hash functions with similar security arguments and performance profiles in hardware could equally be applied.

### 2020-09-21 tex/related-works.tex
corrected the paper to suit comments from Reviewer 1, also updated this in the response to reviewers txt file

In this section we provide some background on previous hardware implementations post-quantum cryptographic schemes, focusing on those which are candidates of NIST's standardization effort. We will elaborate more FrodoKEM and its implementations as well as recalling the principles of masking.

@@

\begin{table*}[tbhp]
%\small
\caption{A summary of the current state-of-the-art of hardware designs of NIST post-quantum candidates, implemented on FPGA.}\label{tab:pqc}
\begin{center}
%\resizebox{0.7\textwidth}{!}{
\noindent\makebox[\textwidth]{
\begin{tabular}{c l l N{5}{0} N{5}{0} N{5}{0} N{3}{0} N{3}{0} N{3}{0} N{5}{0}}
\hline \Tstrut
&  {\bf Cryptographic Implementation} 
&  {\bf Device}
&  \multicolumn{1}{r}{\bf LUT} 
&  \multicolumn{1}{r}{\bf FF} 
&  \multicolumn{1}{r}{\bf Slice} 
&  \multicolumn{1}{r}{\bf DSP} 
&  \multicolumn{1}{r}{\bf BRAM} 
&  \multicolumn{1}{r}{\bf MHz} 
&  \multicolumn{1}{r}{\bf Thr-Put} \\
\hline \Tstrut
\parbox[t]{5mm}{\multirow{1}{*}{\rotatebox[origin=c]{90}{H}}} & \textsf{SPHINCS-256} (Total) \cite{amiet2018fpga} & Kintex-7 & 19067 & 3132 & 7306 & 3 & 36 & 525 & 654 \\ \hline 	\Tstrut
 \parbox[t]{5mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Code}}} & \textsf{Niederreiter} KeyGen \cite{wang2018fpga} & Stratix-V & \multicolumn{1}{c}{$-$} & \multicolumn{1}{c}{$-$} & 39122 & \multicolumn{1}{c}{$-$} & 827 & 230 & 75 \\
& \textsf{Niederreiter} Encrypt \cite{wang2018fpga} & Stratix-V & \multicolumn{1}{c}{$-$} & 6977 & 4276 & \multicolumn{1}{c}{$-$} & 0 & 448 & 50000 \\
& \textsf{Niederreiter} Decrypt \cite{wang2018fpga} & Stratix-V & \multicolumn{1}{c}{$-$} & 48050 & 20815 & \multicolumn{1}{c}{$-$} & 88 & 290 & 12500 \\ 	
\hline \Tstrut
 \parbox[t]{5mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Isogeny}}} & \textsf{SIKE} 3-cores (Total) \cite{koziel2018high}  & Virtex-7 & 27713 & 38489 & 11277 & 288 & 61 & 205 & 27 \\
& \textsf{SIKE} 6-cores (Total) \cite{koziel2018high} & Virtex-7 & 50084 & 69054 & 19892 & 576 & 55 & 202 & 32 \\  \cline{2-10} \Tstrut
& \textsf{SIKE} 3-cores (Total) \cite{cryptoeprint:2019:568} & Virtex-7 & 49099 & 62124 & 18711 & 294 & 23 & 226 & 32 \\
\hline \Tstrut
 \parbox[t]{5mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Lattice}}} & \textsf{NewHope} KEX Server \cite{cryptoeprint:2017:690}   & Artix-7   & 20826 & 9975 & 7153 & 8 & 14 & 131 & 13699 \\
& \textsf{NewHope} KEX Client \cite{cryptoeprint:2017:690}   & Artix-7   & 18756 & 9412 & 6680 & 8 & 14 & 133 & 12723 \\ \cline{2-10} \Tstrut
& \textsf{NewHope} KEX Server \cite{oder2017implementing}   & Artix-7   & 5142 & 4452 & 1708 & 2 & 4 & 125 & 731 \\
& \textsf{NewHope} KEX Client \cite{oder2017implementing}  & Artix-7   & 4498 & 4635 & 1483 & 2 & 4 & 117 & 653 \\ \cline{2-10} \Tstrut
%& \textsf{Round5} (All) (SoC) [PQShield]  & Art-7  & 7168 & 3337 & 2344 & 0 & \multicolumn{1}{c}{$-$} & 100 & \multicolumn{1}{c}{$-$} \\ \cline{2-10} \Tstrut
& \textsf{FrodoKEM}-640 KeyGen \cite{howe2018standard} & Artix-7 & 3771 & 1800 & 1035 & 1 & 6 & 167 & 51 \\
& \textsf{FrodoKEM}-640 Encaps \cite{howe2018standard}  & Artix-7 & 6745 & 3528 & 1855 & 1 & 11 & 167 & 51 \\
& \textsf{FrodoKEM}-640 Decaps \cite{howe2018standard}  & Artix-7 & 7220 & 3549 & 1992 & 1 & 16 & 162 & 49 \\ \hline \Tstrut
 \parbox[t]{5mm}{\multirow{2}{*}{\rotatebox[origin=c]{90}{OWF}}} & \textsf{Picnic}-L1 Sign \cite{kales2020efficient} & Artix-7 & 76472 & 21061 & \multicolumn{1}{c}{$-$} & \multicolumn{1}{c}{$-$} & 53 & 125 & 3994 \\
& \textsf{Picnic}-L1 Verify \cite{kales2020efficient} & Artix-7 & 68614 & 16821 & \multicolumn{1}{c}{$-$} & \multicolumn{1}{c}{$-$} & 34 & 125 & 4223 \\ 	
\hline
\end{tabular}}%}
\end{center}
\end{table*}

>>>>

In this section we provide some background on previous hardware implementations post-quantum cryptographic schemes, focusing on those which are candidates of NIST's standardization effort. We will also elaborate more on FrodoKEM and its implementations as well as recalling the principles of masking.

@@

\begin{table*}[tbhp]
%\small
\caption{A summary of the current state-of-the-art of hardware designs of NIST post-quantum candidates, implemented on FPGA.}\label{tab:pqc}
\begin{center}
%\resizebox{0.7\textwidth}{!}{
\noindent\makebox[\textwidth]{
\begin{tabular}{c l l N{5}{0} N{5}{0} N{5}{0} N{3}{0} N{3}{0} N{3}{0} N{5}{0}}
\hline \Tstrut
&  {\bf Crypto. Implementation} 
&  {\bf Device}
&  \multicolumn{1}{r}{\bf LUT} 
&  \multicolumn{1}{r}{\bf FF} 
&  \multicolumn{1}{r}{\bf Slice} 
&  \multicolumn{1}{r}{\bf DSP} 
&  \multicolumn{1}{r}{\bf BRAM} 
&  \multicolumn{1}{r}{\bf MHz} 
&  \multicolumn{1}{r}{\bf Ops/Sec} \\
\hline \Tstrut
 \parbox[t]{5mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Code}}} & \textsf{Niederreiter} KeyGen \cite{wang2018fpga} & Stratix-V & \multicolumn{1}{c}{$-$} & \multicolumn{1}{c}{$-$} & 39122 & \multicolumn{1}{c}{$-$} & 827 & 230 & 75 \\
& \textsf{Niederreiter} Encrypt \cite{wang2018fpga} & Stratix-V & \multicolumn{1}{c}{$-$} & 6977 & 4276 & \multicolumn{1}{c}{$-$} & 0 & 448 & 50000 \\
& \textsf{Niederreiter} Decrypt \cite{wang2018fpga} & Stratix-V & \multicolumn{1}{c}{$-$} & 48050 & 20815 & \multicolumn{1}{c}{$-$} & 88 & 290 & 12500 \\ 	
\hline \Tstrut
 \parbox[t]{5mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Isogeny}}} & \textsf{SIKE} 3-cores (Total) \cite{koziel2018high}  & Virtex-7 & 27713 & 38489 & 11277 & 288 & 61 & 205 & 27 \\
& \textsf{SIKE} 6-cores (Total) \cite{koziel2018high} & Virtex-7 & 50084 & 69054 & 19892 & 576 & 55 & 202 & 32 \\  \cline{2-10} \Tstrut
& \textsf{SIKE} 3-cores (Total) \cite{cryptoeprint:2019:568} & Virtex-7 & 49099 & 62124 & 18711 & 294 & 23 & 226 & 32 \\
\hline \Tstrut
 \parbox[t]{5mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Lattice}}} & \textsf{NewHope} KEX Server \cite{cryptoeprint:2017:690}   & Artix-7   & 20826 & 9975 & 7153 & 8 & 14 & 131 & 13699 \\
& \textsf{NewHope} KEX Client \cite{cryptoeprint:2017:690}   & Artix-7   & 18756 & 9412 & 6680 & 8 & 14 & 133 & 12723 \\ \cline{2-10} \Tstrut
& \textsf{NewHope} KEX Server \cite{oder2017implementing}   & Artix-7   & 5142 & 4452 & 1708 & 2 & 4 & 125 & 731 \\
& \textsf{NewHope} KEX Client \cite{oder2017implementing}  & Artix-7   & 4498 & 4635 & 1483 & 2 & 4 & 117 & 653 \\ \cline{2-10} \Tstrut
%& \textsf{Round5} (All) (SoC) [PQShield]  & Art-7  & 7168 & 3337 & 2344 & 0 & \multicolumn{1}{c}{$-$} & 100 & \multicolumn{1}{c}{$-$} \\ \cline{2-10} \Tstrut
& \textsf{FrodoKEM}-640 KeyGen \cite{howe2018standard} & Artix-7 & 3771 & 1800 & 1035 & 1 & 6 & 167 & 51 \\
& \textsf{FrodoKEM}-640 Encaps \cite{howe2018standard}  & Artix-7 & 6745 & 3528 & 1855 & 1 & 11 & 167 & 51 \\
& \textsf{FrodoKEM}-640 Decaps \cite{howe2018standard}  & Artix-7 & 7220 & 3549 & 1992 & 1 & 16 & 162 & 49 \\ \hline \Tstrut \Tstrut
\parbox[t]{5mm}{\multirow{1}{*}{\rotatebox[origin=c]{90}{H}}} & \textsf{SPHINCS-256} (Total) \cite{amiet2018fpga} & Kintex-7 & 19067 & 3132 & 7306 & 3 & 36 & 525 & 654 \\ \hline 	\Tstrut
 \parbox[t]{5mm}{\multirow{2}{*}{\rotatebox[origin=c]{90}{OWF}}} & \textsf{Picnic}-L1 Sign \cite{kales2020efficient} & Artix-7 & 76472 & 21061 & \multicolumn{1}{c}{$-$} & \multicolumn{1}{c}{$-$} & 53 & 125 & 3994 \\
& \textsf{Picnic}-L1 Verify \cite{kales2020efficient} & Artix-7 & 68614 & 16821 & \multicolumn{1}{c}{$-$} & \multicolumn{1}{c}{$-$} & 34 & 125 & 4223 \\
\hline \Bstrut
\end{tabular}}%}
\end{center}
\end{table*}
